Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1].}

### 2018-11-18 paper/paper.tex
More plottery

\begin{abstract}
    The current state of the art in subgraph isomorphism solving involves using degree as a
    value-ordering heuristics to direct backtracking search. Such a search makes a heavy commitment
    to the first branching choice, which is often incorrect. We evaluate discrepancy-based searches
    as an alternative, but find them too expensive to be effective in this situation, even on
    satisfiable instances. We then demonstrate that a random value-ordering heuristic with restarts
    beats conventional search with the best-known tailored heuristic. This motivates the
    introduction of a novel slightly-random heuristic with similar behaviour to the tailored
    heuristic: when combined with restarts and nogood recording, this new search strategy is over ??
    times more effective on satisfiable instances, and does not affect performance on
    unsatisfiable instances. Such a search can also be parallelised in a way which is much
    simpler than conventional work-stealing: we obtain further speedups of ??  on ??  cores, and
    ?? over ?? distributed-memory hosts. Finally, we show that this search strategy also improves
    two maximum common induced subgraph algorithms.
\end{abstract}

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-parallel.pdf}

@@

@@

>>>>

\begin{abstract}
    The current state of the art in subgraph isomorphism solving involves using degree as a
    value-ordering heuristic to direct backtracking search. Such a search makes a heavy commitment
    to the first branching choice, which is often incorrect. To mitigate this, we introduce and
    evaluate a new approach, which we call ``solution-biased search''. By combining a
    slightly-random value-ordering heuristic, rapid restarts, and nogood recording, we achieve two
    orders of magnitude faster performance on satisfiable instances, whilst not affecting
    performance on unsatisfiable instances. This search can also be parallelised in a very simple
    but effective way, giving us a further speedup of over thirty from thirty-six cores, across both
    satisfiable and unsatisfiable instances.  Finally, we show that solution-biased search is also
    suitable for optimisation problems, by using it to improve two maximum common induced subgraph
    algorithms.
\end{abstract}

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-parallel.pdf}

@@

    \includegraphics*{gen-graph-scatter-par-repeat.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-parconsttick-repeat.pdf}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-parconst-nodes.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-parconsttick-nodes.pdf}

    \caption{Parallel nodes}\label{figure:parallelnodes}
\end{figure}
